IML Term project

### 2022-12-11 main_markdown.rmd

mean(as.numeric(multinb.pred.loocv == npf.class4$class4))
```
### LDA on the npf.168-dataset

@@

@@

mean(as.numeric(multiqda.pred.loocv == npf.pca.class4$class4))
```

### QDA on the npf.168.pca-dataset

@@

mean(as.numeric(multiqda.pred.loocv == npf.168.pca.class4$class4))
```
### GLM
```{r glm, warning=FALSE, fig.height=4}
mod1<-glm(class2~., npf, family=binomial(link="logit"))
mod2<-glm(class2~., npf, family=binomial(link="probit"))
plot(mod1)
prob1<-predict(mod1, npf, type="response")
pred1<-c()
perp1<-c()
for(i in 1:dim(npf)[1]){
  if(prob1[i]>=0.5){
    pred1<-c(pred1,1)
  } else{
    pred1<-c(pred1,0)
  }
  if(npf$class2[i]==1){
    perp1<-c(perp1,prob1[i])
  } else{
    perp1<-c(perp1,1-prob1[i])
  }
}
```

>>>>

mean(as.numeric(multinb.pred.loocv == npf.class4$class4))
```

Class-specific accuracies in the order Ia, Ib, II, nonevent.

```{r naive bayes multiclass by class, warning=FALSE, fig.height=4}

mean(as.numeric(multinb.pred.loocv[which(npf.class4$class4 == "Ia")] == npf.class4$class4[which(npf.class4$class4 == "Ia")]))
mean(as.numeric(multinb.pred.loocv[which(npf.class4$class4 == "Ib")] == npf.class4$class4[which(npf.class4$class4 == "Ib")]))
mean(as.numeric(multinb.pred.loocv[which(npf.class4$class4 == "II")] == npf.class4$class4[which(npf.class4$class4 == "II")]))
mean(as.numeric(multinb.pred.loocv[which(npf.class4$class4 == "nonevent")] == npf.class4$class4[which(npf.class4$class4 == "nonevent")]))

### LDA on the npf.168-dataset

@@

Class-specific accuracies in the order Ia, Ib, II, nonevent.

```{r lda multiclass by class, warning=FALSE, fig.height=4}

mean(as.numeric(multilda.pred.loocv[which(npf.class4$class4 == "Ia")] == npf.class4$class4[which(npf.class4$class4 == "Ia")]))
mean(as.numeric(multilda.pred.loocv[which(npf.class4$class4 == "Ib")] == npf.class4$class4[which(npf.class4$class4 == "Ib")]))
mean(as.numeric(multilda.pred.loocv[which(npf.class4$class4 == "II")] == npf.class4$class4[which(npf.class4$class4 == "II")]))
mean(as.numeric(multilda.pred.loocv[which(npf.class4$class4 == "nonevent")] == npf.class4$class4[which(npf.class4$class4 == "nonevent")]))

@@

mean(as.numeric(multiqda.pred.loocv == npf.pca.class4$class4))
```
Class-specific accuracies in the order Ia, Ib, II, nonevent.

```{r qda multiclass by class, warning=FALSE, fig.height=4}

mean(as.numeric(multiqda.pred.loocv[which(npf.class4$class4 == "Ia")] == npf.class4$class4[which(npf.class4$class4 == "Ia")]))
mean(as.numeric(multiqda.pred.loocv[which(npf.class4$class4 == "Ib")] == npf.class4$class4[which(npf.class4$class4 == "Ib")]))
mean(as.numeric(multiqda.pred.loocv[which(npf.class4$class4 == "II")] == npf.class4$class4[which(npf.class4$class4 == "II")]))
mean(as.numeric(multiqda.pred.loocv[which(npf.class4$class4 == "nonevent")] == npf.class4$class4[which(npf.class4$class4 == "nonevent")]))

```
### QDA on the npf.168.pca-dataset

@@

mean(as.numeric(multiqda.pred.loocv == npf.168.pca.class4$class4))
```

```{r qda multiclass 168 by class, warning=FALSE, fig.height=4}

mean(as.numeric(multiqda.pred.loocv[which(npf.class4$class4 == "Ia")] == npf.class4$class4[which(npf.class4$class4 == "Ia")]))
mean(as.numeric(multiqda.pred.loocv[which(npf.class4$class4 == "Ib")] == npf.class4$class4[which(npf.class4$class4 == "Ib")]))
mean(as.numeric(multiqda.pred.loocv[which(npf.class4$class4 == "II")] == npf.class4$class4[which(npf.class4$class4 == "II")]))
mean(as.numeric(multiqda.pred.loocv[which(npf.class4$class4 == "nonevent")] == npf.class4$class4[which(npf.class4$class4 == "nonevent")]))

### GLM
```{r glm, warning=FALSE, fig.height=4}
mod1<-glm(class2~., npf, family=binomial(link="logit"))
mod2<-glm(class2~., npf, family=binomial(link="probit"))
plot(mod1)
prob1<-predict(mod1, npf, type="response")
pred1<-c()
perp1<-c()
for(i in 1:dim(npf)[1]){
  if(prob1[i]>=0.5){
    pred1<-c(pred1,1)
  } else{
    pred1<-c(pred1,0)
  }
  if(npf$class2[i]==1){
    perp1<-c(perp1,prob1[i])
  } else{
    perp1<-c(perp1,1-prob1[i])
  }
}
```
